Implementing \Kwd{DNS} in \Kwd{C0}

### 2017-12-13 paper.tex
fix figure refs

We began by testing with the default settings of \Kwd{resperf}, wherein the number of queries being sent per second increases linearly from 0 to 100,000 over the course of a minute. We found, however, that this did not yield useful results, as the throughput capacity of \Kwd{c0ns} is so low by comparison. After adjusting parameters to get useful data, we found that setting a maximum of 100 queries per second over the same time interval of 60 seconds was suitable. We then tested both the checked (safe) and unchecked (not safe) versions of \Kwd{c0ns} with these parameters. Interestingly, the difference between the performance of the checked version (shown in Figure~\cite{fig:checked-perf}) and the performance of the unchecked version (shown in Figure~\cite{fig:unchecked-perf}) was minimal, suggesting that contract-checking provides little to no overhead at these speeds (though it is likely that with higher base throughput, the difference would become more evident).

>>>>

We began by testing with the default settings of \Kwd{resperf}, wherein the number of queries being sent per second increases linearly from 0 to 100,000 over the course of a minute. We found, however, that this did not yield useful results, as the throughput capacity of \Kwd{c0ns} is so low by comparison. After adjusting parameters to get useful data, we found that setting a maximum of 100 queries per second over the same time interval of 60 seconds was suitable. We then tested both the checked (safe) and unchecked (not safe) versions of \Kwd{c0ns} with these parameters. Interestingly, the difference between the performance of the checked version (shown in Figure~\ref{fig:checked-perf}) and the performance of the unchecked version (shown in Figure~\ref{fig:unchecked-perf}) was minimal, suggesting that contract-checking provides little to no overhead at these speeds (though it is likely that with higher base throughput, the difference would become more evident).
